\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-26 paper/ms.tex
show only one f_CZ

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank_vari.pdf}
  \caption{Expected differences in solar abundances after adding
    varying mass of bulk Earth material.
    Elements are ordered by their $T_C$ on $x$-axis, same as
    \figname~\ref{fig:deltaxh_tcrank}.
    The solid and dashed lines assume $f_\mathrm{CZ}=0.02$ and $f_\mathrm{CZ} =
    0.03$ respectively.
    For each $f_\mathrm{CZ}$, we show expected $\Delta\elemH{X}$
    for adding 5, 10, 15, 20, 25~\mearth\ of bulk Earth (from bottom to top).
  }
  \label{fig:vari}
\end{figure}

@@

The estimate of accreted mass depends sensitively on $f_\mathrm{CZ}$ and the
mass of the star which are difficult quantities to constrain directly through
data.
While we adopt $(f_\mathrm{CZ},\,M) = (0.02, 1~M_\odot)$, we show the
expected changes in $\Delta\elemH{X}$ for $f_\mathrm{CZ}=0.03$ in
\figname~\ref{fig:vari}.

>>>>

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank_vari.pdf}
  \caption{Expected differences in solar abundances after adding
    varying mass of bulk Earth material.
    Elements are ordered by their $T_C$ on $x$-axis, same as
    \figname~\ref{fig:deltaxh_tcrank}.
    We assume $f_\mathrm{CZ} = 0.02$ and show expected $\Delta\elemH{X}$
    for adding 5, 10, 15, 20, 25~\mearth\ of bulk Earth (from bottom to top).
  }
  \label{fig:vari}
\end{figure}

@@

The estimate of accreted mass depends sensitively on $f_\mathrm{CZ}$ and the
mass of the star which are difficult quantities to constrain directly through
data.
We adopt $(f_\mathrm{CZ},\,M) = (0.02, 1~M_\odot)$, and show
expected changes for the accretion of $5-25$~\mearth\ of bulk Earth material
in \figname~\ref{fig:vari}.
However, we note that if $f_\mathrm{CZ}$ is $0.03$, the estimate for the accreted
mass would be $\approx 20$~\mearth.
